---
title: "crz"
output: 
  flexdashboard::flex_dashboard:
    orientation: rows
date: '2022-03-29'
---

```{r = global, setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE)
library(flexdashboard)
library(knitr)
#library(shiny)
```

## ss

### ssss
```{r}
valueBox(107, caption = "Trials", icon="fa-tag")
```

### sdds
```{r}
valueBox("Ahoj", icon = "fa-comments")
```

### dfffrfrfr
```{r}
valueBox(value = "Hi", icon = "fa-comments")
```



## Inputs and Outputs

### dfffrfrfr
This R Markdown **document** is made *interactive* using Shiny. Unlike the more traditional workflow of creating static reports, you can now create documents that allow your readers to change the assumptions underlying your analysis and see the results immediately.

### dfffrfrfr
To learn more, see [Interactive Documents](http://rmarkdown.rstudio.com/authoring_shiny.html).


## Inputs and Outputs

### Chart 1

You can embed Shiny inputs and outputs in your document. Outputs are automatically updated whenever inputs change. This demonstrates how a standard R plot can be made interactive by wrapping it in the Shiny `renderPlot` function. The `selectInput` and `sliderInput` functions create the input widgets us

### Chart 2

sdsds sdsdd sdsd sddsdsdsds

### Chart 2

sdsds sdsdd sdsd sddsdsdsds

